Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-01 paper/paper_new.tex
Brightness section

\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
    {\footnotesize \thanks{NSF Grant ???} }}
%do we add grant now, or wait til acceptance. i think we need to ultimately remove any identifying info., i think bgnn is likely okay; but, perhaps mention metadata research center (MRC) need to be removed?. if so, i kind of like to put it back in for final version, if accepted. it helps with getting funding ... you are both listed on the MRC page. we should check on the identifying info. removed, or not.
%for the record: Research supported by NSF OAC #1940233 and #1940322.

@@

%\begin{wraptable}{r}{5.5cm}
\begin{table}[H]
    \centering
      \caption{Training dataset}
    \label{tab:dataset}
    \begin{tabular}{cc}
        \toprule
        \textbf{Class} & \textbf{Number of Instances}\\
        \midrule
        Fish & 297\\
        Ruler & 1496\\
        Eye & 456\\
        Two & 100\\
        Three & 100\\
      \bottomrule
    \end{tabular}
\end{table}
%\end{wraptable}

@@

\subsection{Foreground/Background Contrast Results?}
\begin{figure}[H]
  \centering
  \includegraphics[width=\linewidth]{images/histo}
  \caption{Histogram for difference in brightness between foreground an background.}
\end{figure}

\subsection{Brightness/Uniformity Results?}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/dark}
  \includegraphics[width=0.49\linewidth]{images/normal}
  \includegraphics[width=0.49\linewidth]{images/bright}
  \caption{Examples of low, normal and high contrast fish images.}
\end{figure}
\textbf{Todo}: It looks like we should leave out Uniformity.

\begin{verbatim}
This is for average foreground intensity
(i.e. the fish pixels)
Mean intensity in bounding box | Std
        | Count

dark: 75.14548320341247 |
        13.491022754871715 | 1800
normal: 93.63755945070938 |
        14.781004083081378 | 5186
bright: 108.39315328695254 |
        15.210726241270661 | 242
\end{verbatim}
\begin{verbatim}
Standard Deviations for:
    Uniform: 12.554834863869324
    Not Uniform: 11.312181711328828
\end{verbatim}

>>>>

\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
    {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }}
%do we add grant now, or wait til acceptance. i think we need to ultimately remove any identifying info., i think bgnn is likely okay; but, perhaps mention metadata research center (MRC) need to be removed?. if so, i kind of like to put it back in for final version, if accepted. it helps with getting funding ... you are both listed on the MRC page. we should check on the identifying info. removed, or not.
%for the record: Research supported by NSF OAC #1940233 and #1940322.

@@

%\begin{wraptable}{r}{5.5cm}
\begin{table}[H]
    \centering
      \caption{Training dataset}
    \label{tab:dataset}
    \begin{tabular}{cccc}
        \toprule
        \textbf{Class} & \textbf{Number of Instances}\\
        \midrule
        Fish & 297\\
        Ruler & 1496\\
        Eye & 456\\
        Two & 100\\
        Three & 100\\
      \bottomrule
    \end{tabular}
\end{table}
%\end{wraptable}

@@

\subsection{Image Contrast}
\begin{figure}[H]
  \centering
  \includegraphics[width=\linewidth]{images/histo}
  \caption{Histogram for difference in brightness between foreground an background.}
  \label{fig:histo}
\end{figure}

The contrast of an image is an important aspect of the image quality for the BGNN study. Ideally, for INHS images the fish should be well lit and vibrant, and the background should also be as light and white as possible. Figure~\ref{fig:histo} shows the distribution of the difference between the mean intensity of the foreground (i.e.\ the pixels of the fish) and the mean intensity of the background within the fish's bounding box. The overall mean of the distribution is \(144.26\), with a standard deviation of \(15.79\). Images on the low end of this distribution exhibit poor foreground--background contrast, and images on the high end likely contain poorly lit specimens. Examples of each type of image (low, normal, and high contrast) can be seen in Figure~\ref{fig:contrast}. The top left image has a mean intensity of 103 (low), the top right 144 (normal), and the bottom 186 (high).

\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/dark}
  \includegraphics[width=0.49\linewidth]{images/normal}
  \includegraphics[width=0.49\linewidth]{images/bright}
  \caption{Examples of low, normal and high contrast fish images.}
  \label{fig:contrast}
\end{figure}

\subsection{Brightness}
Specimen brightness is one of the 22 hand recorded properties. It is encoded as \verb|dark|, \verb|normal| or \verb|bright|. These values correspond to the measurement of mean foreground intensity by the automated system. The correlation between the two measurements can be seen in Table~\ref{tab:bright} below.
\begin{table}[H]
    \centering
    \caption{Brightness measurements}
    \label{tab:bright}
    \begin{tabular}{cccc}
        \toprule
        \textbf{Class} & \textbf{Mean Intensity} & \textbf{Standard Deviation} & \textbf{Instances}\\
        \midrule
        Dark & 75.15 & 13.49 & 1800\\
        Normal & 93.64 & 14.78 & 5186\\
        Bright & 108.39 & 15.21 & 242\\
        \bottomrule
    \end{tabular}
\end{table}

\textbf{Todo}: I suppose more should be said here.

%\begin{verbatim}
%Standard Deviations for:
    %Uniform: 12.554834863869324
    %Not Uniform: 11.312181711328828
%\end{verbatim}
